Semantic Photographic Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-10-16 cvpr2018.tex
2nd v

Generative adversarial networks (GANs) have become the main solution to this task. 
Scott \etal \cite{reed2016generative} takes the first step to address this task through a GAN based framework, which is similar with DCGAN \cite{}. But this method only handles image up to $64{\times}64$ resolution and usually is barely to generate vivid object details.
Based on \cite{reed2016generative}, Zhang \etal \cite{} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images. This method needs individual two-stage training, which is relatively not straightforward to be applied. Later on, Dong \etal \ref{dong2017semantic} 
bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training image according to targeting semantic descriptions. However, the high resolution synthesis ability is still indeterminate. 
Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$)  images is still an open question according to current reported studies.

We outline several empirical reasons for this challenges using GANs. The first fundamental problem comes from the difficulty of balancing the stability between generators and discriminators. There are many a rich number of literature trying to stabilize GAN training \cite{}. But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators.

With careful consideration of these reasons, in our method, we propose a novel method that can directly generate high resolution images trained in fully end-to-end fashion. To tackle the significant space difference between text and images, we propose to leverage the hierarchical deep representations of convolutional layers through deeply compositional constraints. In other words, we limit feature maps in different layers to be disentangled RGB image space, such that feature maps of any layers can linearly represent targeting images at corresponding resolutions. We introduce accompanying adversarial objective at deep layers to achieve this goal, inspired by the deeply-supervised nets (DSN) \cite{lee2015deeply} for image classification.
In difference of previous methods, our method has an intuitive network architecture design with hierarchically-nested adversarial objectives that is more efficient and faster to train.

To tackle the instability training of GANs, \textcolor{red}{we enforce discriminators at different resolutions can differentiate real/fake image, correct/incorrect image-text pairs, and real/fake image pairs jointly. This multi-purpose strategy is mutually beneficially }

>>>>

Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} takes the first step to address this task through a GAN based framework. But this method only handles image up to $64{\times}64$ resolution and usually is barely to generate vivid object details.
Based on \cite{reed2016generative}, Zhang \etal \cite{han2017stackganan} present a successful approach (StackGAN) by stacking another GAN to generate high quality and compelling $256{\times}256$ images given inputs of low resolution $64{\times}64$ synthetic images. This method needs individual two-stage training, which is relatively not straightforward to be applied. Later on, Dong \etal \ref{dong2017semantic} 
bypasses the difficult of translate vector semantic vector to RGB image and treat it as an pixel-to-pixel translation \cite{isola2016image}, by re-renders a arbitrary-style training image according to targeting semantic descriptions. However, the high resolution synthesis ability is still indeterminate. 
Unfortunately, directly training from vector space and synthesize high resolution (e.g. $256{\times}256$)  images is still an open question according to current reported studies.

We outline several empirical reasons for this challenges using GANs. The first fundamental problem comes from the difficulty of balancing the stability between generators and discriminators. There are many a rich number of literature trying to stabilize GAN training \cite{salimans2016improved}. But especially for text-to-image synthesis, how to utilize the multimodal information between images and text in discriminator is extremely important and needs careful consideration. The second reason is that the pixel space in high resolution image is substantially large \cite{han2017stackgan}. Keeping semantic consistency as well as diversity in generated images needs more specialized designs for discriminators.

With careful consideration of these reasons, in this paper, we propose a novel method that can directly generate high resolution images trained in fully end-to-end fashion. The contributions are described follows.

To tackle the problem of significant space difference between text and images, we propose to leverage the hierarchical deep representations of convolutional layers through deeply compositional constraints. In other words, we limit feature maps in different layers to be disentangled RGB image space, such that feature maps of any layers can linearly represent targeting images at corresponding resolutions. We introduce accompanying deeply-nested adversarial objective at intermediate layers to achieve this goal, inspired by the deeply-supervised nets (DSN) \cite{lee2015deeply} for image classification.
To well cooperate with discriminators, we propose an intuitive network architecture design with hierarchically-nested adversarial objectives that is more efficient and faster to train.

To tackle the instability training of GANs, \textcolor{red}{we propose to enforce discriminators at different resolutions can differentiate real/fake image, correct/incorrect image-text pairs, and real/fake image pairs jointly with multiple losses.} We will show that this multi-purpose strategy is mutually beneficially to encourage them only focus on respect duty. It is a regularization to limit the discriminators to use unexpected information to make decision.

We have validated our proposed method on three datasets, i.e. CUB birds, Oxford-102 flowers, and large-scale COCO datasets. Extensive experimental results demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts.

\section{Related Work}
There are substantial existing methods investigating better usage of GANs \cite{goodfellow2014generative,radford2015unsupervised} for different applications, such as image synthesis \cite{shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired},  medical imaging \cite{costa2017towards}, etc \cite{}.

Text-to-image synthesis is one of the most challenging tasks requires accurate semantically consistent mapping from a text vector space to a much higher image space.  Reed \etal \cite{reed2016generative} introduces the first method that can generate $64{\times}64$ resolution images, which is similar with DCGAN \cite{}. This method presents a new strategy to image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose  generative
adversarial what-where network (GAWWN) to enable "where and what" instructions in text-to-image synthesis, which uses extra information to help generate $128{\times}128$ resolution images. StackGAN \etal \cite{han2017stackgan} propose to a two-stage stacking GAN training approach that is able to generate $256{\times}256$ high resolution vivid images. Recently, \cite{dong2017semantic} proposes to learn a joint embedding of images and text so as to re-render a prototype image according to targeting descriptions.

GANs suffer from optimization difficulties. Wide methods have been proposed to stabilize the training process, for example, one-side label smoothing and discriminator feature matching \cite{salimans2016improved}, training stronger discriminator is beneficial to encourage generators \cite{arjovsky2017wasserstein}. Balancing through a equilibrium enforcing method \cite{berthelot2017began}
Preventing discriminators from forgetting past samples and re-introduces artifacts \cite{shrivastava2016learning}. Increasing the information richness in GANs has been shown very useful \cite{odena2016conditional}.

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks like image classification \cite{lee2015deeply} and edge detection \cite{xie2015holistically}. DSN \cite{lee2015deeply} introduces deep supervision in hierarchical convolutional layers to increase the discriminativenss of feature representations. In aspect of unsupervised learning, Denton \etal \cite{denton2015deep} trains a cascade of GANs within a Laplacian pyramid framework (LAPGAN) and use each to generate difference images conditioned on noise and images from last pyramid, and gradually increase image resolution. StackGAN also shares similar strategy with LAPGAN to increase output resolution. Different from these methods,

deep supervision
